---
title: "Congressional Trades as an Index Fund"
author:
  - "Mark Newman"
date: "2022/08/31"
editor_options: 
  chunk_output_type: console
---

Setup location and clear out all existing variables

```{r}
here::i_am('index.rmd')
rm(list = ls())
```

Add in all the libraries we need

```{r message = F, warning = F}
library(here)
library(rvest)
library(dplyr)
library(crul)
library(stringr)
library(lubridate)
```

Setup the root URLs and paths

```{r}
year <- year(today())
root_url <- 'https://disclosures-clerk.house.gov'
zip_dir <- here('cache/zip')
pdf_dir <- here('cache/pdf')
txt_dir <- here('cache/txt')
```

Setup the HTTP Client

```{r}
client <- HttpClient$new(url = root_url)
```
```{r echo = F}
rm(root_url)
```

Make sure the `pdf_dir` exists

```{r echo = !dir.exists(pdf_dir), eval = !dir.exists(pdf_dir)}
if(!dir.exists(pdf_dir)) {
  dir.create(pdf_dir, recursive = T)
}
```

Make sure the `zip_dir` exists

```{r echo = !dir.exists(zip_dir), eval = !dir.exists(zip_dir)}
if(!dir.exists(zip_dir)) {
  dir.create(zip_dir, recursive = T)
}
```

Make sure the `txt_dir` exists

```{r echo = !dir.exists(txt_dir), eval = !dir.exists(txt_dir)}
if(!dir.exists(txt_dir)) {
  dir.create(txt_dir, recursive = T)
}
```

Check to see if we need to re-retrieve the yearly zip file.

```{r}
yearly_file <- str_glue('{zip_dir}/{year}FD.txt')

check_cache <- file.exists(yearly_file)
needs_refresh <- !check_cache
```

```{r echo = check_cache, eval = check_cache}
if(check_cache) {
  data <- read.delim(yearly_file)
  data <-
    data %>%
    mutate(
      FilingDate = mdy(FilingDate)) %>%
    filter(!is.na(FilingDate))
  needs_refresh <- 
    !(max(data$FilingDate) >= (today() - ddays(x = 1)))
  rm(data)
}
```
```{r echo = F}
rm(check_cache)
```

If necessary, (re)retrieve the yearly zip file

```{r echo = needs_refresh, eval = needs_refresh}
if(needs_refresh) {
  zip_url <-  str_glue('/public_disc/financial-pdfs/{year}FD.ZIP')
  zip_file <- str_glue('{zip_dir}/{year}FD.ZIP')
  res <- client$get(path = zip_url, disk = zip_file)
  unzip(zip_file, exdir = zip_dir)
  rm(zip_url, zip_file, res)
}
```
```{r echo = F}
rm(needs_refresh)
```

Load the yearly data

```{r}
data <- read.delim(yearly_file)
data <-
  data %>%
  mutate(
    FilingDate = mdy(FilingDate)) %>%
  filter(!is.na(FilingDate)) %>%
  filter(FilingType == 'P')
```
```{r echo = F}
rm(yearly_file)
```

Loop through the `DocID`s to get all the PDFs

```{r}
if(interactive()) { pb <- txtProgressBar(max = nrow(data), style = 3) }
for(i in 1:nrow(data)) {
  id <- data$DocID[i]
  pdf_url <- str_glue('/public_disc/ptr-pdfs/{year}/{id}.pdf')
  pdf_file <- str_glue('{pdf_dir}/{id}.pdf')
  if(!file.exists(pdf_file)) {
    res <- client$get(path = pdf_url, disk = pdf_file)
    Sys.sleep(5)
    rm(res)
  }
  if(interactive()) { setTxtProgressBar(pb, i) }
  rm(pdf_url, pdf_file)
}
if(interactive()) {
  close(pb)
  rm(pb)
}
rm(i)
```
